### 2019-10-04 vesicle_code/docs/softmatter/permeableVes.tex
added new references

>>>>

  \item Loitto et al.~\cite{loi-kar-mag2009} give a review article
    concerning the water flux and its effects on cell motility and
    membrane protrusion. They discuss the role of aquaporins.

  \item In~\cite{tha-kum-mad-pul2006}, they show experimental results of
    self-driven drops. They also compare the experiment with numerical
    results.

  \item Khair~\cite{kha2013} models and simulates diffusiophoresis at a
    variety of Peclet numbers. In Section 5, he provides estimates for
    the self-driven velocity of a non-spherical colloid at finite Peclet
    number.

  \item Keh and Tu~\cite{keh-tu2000} consider osmophoresis of one and
    two spherical vesicles.  Two vesicles are simulated using the method
    of reflections. They consider the zero Peclet number limit which is
    the limit Ashley and Bryan plan to simulate in the next paper.
    However, they assume the vesicle is nearly spherical so that
    standard basis functions can be used. Using a BIE would still be
    new.
